### 2021-04-08 final-report.latex/main.tex
add code to appendix

\appendix
\chapter{C++ NLSM Monte Carlo Program}
\lstset{language=C++,
                basicstyle=\ttfamily,
                keywordstyle=\color{blue}\ttfamily,
                stringstyle=\color{red}\ttfamily,
                commentstyle=\color{green}\ttfamily,
                morecomment=[l][\color{magenta}]{\#}
}

>>>>

\appendix
\chapter{C++ NLSM Monte Carlo Program}
\lstset{language=C++,
                basicstyle=\small\ttfamily,
                keywordstyle=\color{blue}\ttfamily,
                stringstyle=\color{red}\ttfamily,
                commentstyle=\color{green}\ttfamily,
                morecomment=[l][\color{magenta}]{\#},
                breaklines=true,
                postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space}
}

\codeexample{sweep.h}
\codeexample{sweep.cpp}
\codeexample{lattice.h}
\codeexample{lattice.cpp}
\codeexample{phi.h}
\codeexample{phi.cpp}
\codeexample{observables.h}
\codeexample{constants.h}
